---
title: "Drug-resistant Extra-pulmonary TB: A scoping review"
author: "Miiro Emmanuel, MD."
format: html
editor: visual
---

# Clinical features, resistance patterns and treatment outcomes of drug-resistant extra-pulmonary tuberculosis: a scoping review

This document has the code necessary to generate the tables in the above paper. Relevant abbreviations: RR, Rifampicin Resistant; MDR, Multi-drug Resistant; pre-XDR, pre-extensively drug-resistant; XDR, extensively drug-resistant; TB, Tuberculosis; PRISMA, Preferred Reporting Items for Systematic Review and Meta-Analyses. \## Read and clean data

```{r}
#| label: fetch-data
#| results: false
#| warning: false
#| message: false
library(tidyverse) # for data wrangling functions
library(conflicted) # for handling conflicts between packages
library(here) # for handling paths
library(knitr)
library(kableExtra)
data <- readxl::read_xlsx(here("data", "Extracted_data.xlsx")) # the data sheet was saved in a folder named 'data'

# clean column names
data <- janitor::clean_names(data)

data$died_n <- as.numeric(data$died_n) # convert died_n column to numeric

# convert n into percentage for the columns reporting resistance and treatment outcomes
data <- data |> mutate(across(c(rif:xdr, surgical_intervention_n:not_treated), ~ round((.x / total_with_resistance * 100), 1)))

```

## Table 1

This table shows characteristics and demographics of the included studies. We did some additional formatting of this table in MS word to insert captions and footnotes.

```{r}
#| label: table-one
data$age_median <- as.character(data$age_median)
data |> select(author, publication_year, country, type_of_study,
         start_of_data_collection, end_of_data_collection, sample_size, total_with_resistance, age_mean, age_median) |> kable()
```

## Table 2

This table was created manually in MS word because it made formatting easier. The variables with the relevant information is `symptoms_n_percent` and `signs_n_percent`. \## Table 3 This table reported the proportion of DR-epTB for each drug and combinations (e.g., MDR, pre-XDR, XDR). Final touches were added in MS word.

```{r}
#| label: table-3

data |> select(author, total_with_resistance, rif:xdr) |> kable()
```

## Table 4

This table reports the treatment outcomes among patients treated for DR-epTB. Finishing touches (e.g., captions, footnotes, etc) were added using MS word.

```{r}
#| label: table-4

data %>%
  select(author, total_with_resistance, cured_completed_treatment_n:not_treated) |> kable()
```

## Figure 1: PRISMA flow diagram

I first download the PRISMA template csv [here](https://estech.shinyapps.io/prisma_flowdiagram/) then edited the csv to include numbers/values/figures relevant to out review. The following code chunk renders the flow diagram.

```{r}
#| label: PRISMA
#| warning: false
library(PRISMA2020)
prisma <- read.csv(here("data", "PRISMA.csv")) |> PRISMA_data()

eptb_flow <- PRISMA_flowdiagram(prisma, interactive = FALSE, previous = FALSE, other = FALSE, side_boxes = TRUE)

PRISMA_save(eptb_flow, filename = here("figures", "flow_diagram.svg"), filetype = "svg", overwrite = TRUE)
```

The packages used in this session are:

```{r}
#| label: session-info

sessioninfo::session_info()
```
